\subsection{High Concept and Themes}

\subsubsection{High Concept}

"The dark lady awaknes" is a 2D-Rpg single player game. The game is set in the Hogwarts's school and its surroundings. The story revolves around Minerva McGonagall, a young promising witch studying hard to become a master of Transfiguration. During her seventh year, she will become friends with a peculiar student, Delphini Lestrange, whose life seems to be wrapped in mystery until her arrival at Hogwarts. Delphini's true goal, which Minerva is unaware of, is to find a promising student in order to help her father Tom Riddle win the First Wizarding War, hoping that will prevent the death of her parents.
Minerva will be shaken when her dear friend Myrtle is found dead in the girls' bathroom, with no suspect. With a void in her heart overwhelmed by sorrow and grief, she cries for help: Delphini and the professor Albus Dumbledore come to her aid in order to discover the truth and find the culprit. However, there was bad blood between Dumbledore and Delphini, since her very arrival at Hogwarts, leading to distrust amongst each other.
Minerva is forced to choose who to believe and discover the truth behind the crime through player's choices: you can take sides with Delphini or with Dumbledore.

\subsubsection{Themes}

\paragraph{Friendship is powerful}
Bonding with others is essential in order to overcome great obstacles and grow in one's life. In our case, the relationship between Minerva and Delphini can make the difference between the safety or the early demise of the Wizarding World as we know it.

\paragraph{Question everything}
It's easy to trust blindfully one person because of a blood or friendship relationship; however, one must always develop a critical eye and be ready to question everything and everyone. Minerva isn't aware she's being brutally manipulated by Delphini, as the latter is by her stepfather Rodolphus: only pondering on it can lead to an early discovery of an impending calamity.

\paragraph{Mistakes happen, everyone deserves a second chance}
If someone truly repents of his misdeeds, he should not be ostracized but helped to redeem himself. Even if Delphini manipulated Minerva, the latter recognizes it was because of her past and her father's influence, eventually forgiving her.

\paragraph{Actions have consequences}
Should Minerva blindly follow Delphini until the very end, she will become a death eater and join Tom Riddle in his escalation for power. On the other hand, if Minerva will be able to find fallacies or contradictions in Delphini's background and motivations, through clues or discussion, she might disrupt the foul plan, potentially saving her friend from hers lust for vengeance.