\pagebreak

\subsection{Teaching Mechanics}

The first level will be a tutorial for the basic controls, including movement and combat.

During the game the player will take part to various lessons, in the form of minigames. These lessons will require the player to use a particular spell to reach the solution (that spell is enabled for the minigame, even if the character doesn't reach its level prerequisites yet).
When a character reaches a new level, only the spells he would unlock at that level which he has already seen at lesson can be assigned to a spell slot. That way for every newly learnt spell, the player will have already tried it once and experienced the way it works.
This is important, especially for utility spells and all spells that have an effect on the world outside of combat.
Similarly, the player will be introduced to the potions brewing mechanic during a lesson, which will require to craft some potion given some ingredients. After that, the player will be able to find other recipes during the game, and he will have to follow their instructions to craft them, like he did during the lesson.
In all the previous points, teacher NPCs serve as mentors, giving the player instructions and hints through the ingame dialogues.
The most peculiar mechanic, Minerva's Animagus transformation, is obtained in the second half of the game; it will be further explained in the Level Design section of this document.

On the contrary, Friendship Points and how they affect Delphini's capabilities are hidden; depending on the player type, some might be interested in delving deeper through multiple runs of the game, while some others might simply enjoy the increase in immersion.

\pagebreak