\pagebreak

\subsection{Levels and Goals Outline}

\paragraph{Level 1:} A quick refresher (tutorial) \textit{[Hogwarts]}
\begin{enumerate}[1)]
	\item Reach the common hall.
	\item Search for your friend Myrtle.
	\item Help her revise for her next exam.
	\begin{enumerate}[1.]
		\item Practice common spells.
		\item Look up on the books for basic potions and its ingredients.
	\end{enumerate}
\end{enumerate}

\paragraph{Level 2:} A friend in need \textit{[Black Lake]}
\begin{enumerate}[1)]
	\item Reach the Black Lake shore to unwind a bit after all that study.
	\item Approach the screaming girl.
	\item Save Myrtle from the mermaid!
	\begin{enumerate}[1.]
		\item Help the girl find her wand stolen by Grindylows.
		\item Interrogate the Grindylows.
		\item Reach the cave for clues.
		\item Release Myrtle and fight the mermaid.
	\end{enumerate}
	\item Bring Myrtle back to the infirmary.
\end{enumerate}

\paragraph{Level 3:} A lesson to remember (hub level) \textit{[Hogwarts, Quidditch Pitch, Hogsmeade, Diagon Alley]}

Classes (minigames), free exploration, shopping.
\begin{enumerate}[1)]
	\item Follow mandatory Transfiguration and Quidditch classes.
\end{enumerate}

\paragraph{Level 4:} A night in the woods \textit{[Forbidden Forest]}
\begin{enumerate}[1)]
	\item Sneak past the professors and the prefects to get out the castle.
	\item Meet up with Delphini and reach the Forbidden Forest.
	\item Practice with her combined spells.
	\item Fight the enraged centaurs on the way back.
\end{enumerate}

\paragraph{Level 5:} Preparing for greatness \textit{[Hogwarts]}
\begin{enumerate}[1)]
	\item Meet with Dumbledore in his office.
	\item Scout for ingredients
	\begin{enumerate}[1.]
		\item Get a mandrake leaf from the Herbology Lab.
		\item Get a teaspoon of "unscathed" dew.
		\item Get a chrysalis of a Death's-head Hawk Moth.
	\end{enumerate}
\end{enumerate}

\paragraph{Level 6:} Waiting for the Storm (hub level) \textit{[Hogwarts, Quidditch Pitch, Hogsmeade, Diagon Alley]}

Classes (minigames), free exploration, shopping

\paragraph{Level 7:} A cat-call \textit{[Forbidden Forest, Hogwarts]}
\begin{enumerate}[1)]
	\item Complete the Animagus ritual in the Forbidden Forest.
	\begin{enumerate}[1.]
		\item Wait for the storm to begin.
		\item Recite the incantation.
	\end{enumerate}
	\item Survive the Cerberus ambush.
	\item Return to dorms.
	\begin{enumerate}[1.]
		\item Steal keys from the caretaker.
		\item Sneak past the caretaker and the prefects.
		\item (Optional) Help Delphini to return to her dorm unseen.
	\end{enumerate}
\end{enumerate}

\paragraph{Level 8:} A ghastly moan (hub level) \textit{[Hogwarts, Quidditch Pitch, Hogsmeade, Diagon Alley]}
Classes (minigames), free exploration, shopping

\begin{enumerate}[1)]
	\item (Optional) Attend to the Quidditch tournament.
	\item Look for Myrtle in the bathrooms in cat form to surprise her.
	\begin{enumerate}[1.]
		\item Escape and avoid the mysterious shadow.
	\end{enumerate}
	\item Inform Dumbledore and Delphini of the incident.
\end{enumerate}

\paragraph{Level 9:} Gnawing uncertainty \textit{[Hogwarts]}
\begin{enumerate}[1)]
	\item Investigate the bathrooms with Delphini for clues.
	\item Confront Dumbledore on what happened to Hagrid.
	\item Gather information on him with Delphini.
	\item Discuss with Delphini
\end{enumerate}

\paragraph{Level 10:} The last stand \textit{[Dumbledore's office, Hogwarts]}
\begin{enumerate}[1)]
	\item Confront Dumbledore with the found clues.
	\item Choose to believe Dumbledore or Delphini.
\end{enumerate}

\clearpage

\paragraph{Scope}

The game is about 8-9 hours long, but this measure is only indicative as it can depend on how much time the player spends exploring, doing optional classes and quidditch and other activities in the hubs.

\begin{table}[htb]
	\begin{tabular}{ll}
		\textbf{Level} & \textbf{Duration} \\
		A quick refresher & 30 min \\
		A friend in need & 1 h \\
		A lesson to remember & 20 min - 2 h \\
		A night in the woods & 1 h \\
		Preparing for greatness & 1 h \\
		Waiting for the Storm & 30 min \\
		A cat-call & 1 h \\
		A ghastly moan & 40 min - 2 h \\
		Gnawing uncertainty & 1 h \\
		 The last stand & 30 min 
	\end{tabular}
\end{table}

\pagebreak