\section{Diagrams}
Here is a comprehensive list of software to be used in this project, along with their version on which they should be used to reduce the possibility of compatibility issues.
\paragraph{.drawio}
Save format for the draw.io software. It works as a source for diagrams, allowing for easy and quick edits when needed. Diagrams are then exported in the .png format
\paragraph{.png}
The image exported from draw.io files to be inserted in the documentation.

\section{Text}
\paragraph{.tex}
LaTeX file extension

\section{Pictures}
Here is a comprehensive list of software to be used in this project, along with their version on which they should be used to reduce the possibility of compatibility issues.
\paragraph{.piskel} Piskel project format that keeps all the editing information.
\paragraph{.pdn} Paint.net format that keeps all the editing information.
\paragraph{..jpg and .png (documentation)} tandard format for images with no constraints (for example for documentation pictures like characters' portrait, settings and so on...)
\paragraph{.drawio} .png (game) \\

Exported image for game usage.
\begin{itemize}
	\item All images have a 32 bits color depth.
	\item Background images: 1920*1080
	\item Tilesets: each tile is 64*64 pixels
	\item Iconset: each tile is 64*64 pixels.
	\item Faceset: each tile is 256*256. Each file must contain different facial expressions for the same character.
	\item  Character set: each tile is 64*64 pixels. A character set must be 60 tiles wide and at most 4 tiles tall.
		\begin{itemize}
			\item Each 60 horizontally consecutive tiles form a contiguous walking animation, with the 2nd one representing the idle state. 
			\item Each row represent an animation; non-rotating objects only have one row
			\item Objects with an animation for each direction have 4 rows in the following order: right, up, left, down
		\end{itemize}
\end{itemize}


\section{Video }
\paragraph{.mkv, .mp4}
		\begin{itemize}
			\item Resolution: 1920*1080
			\item FPS: 60
			\item Audio Sample Rate: 48000 Hz
			\item Audio Channels: Stereo
		\end{itemize}


\section{Audio }
\paragraph{.ogg Vorbis Audio File}
		\begin{itemize}
			\item Audio Channels: Stereo
			\item Sample Rate: 44100 Hz
			\item Nominal Bitrate: 64 kbit/s
		\end{itemize}

\section{Game data}
\paragraph{.rpgproject}
		 Main project file for RPG Maker MV software 

\paragraph{.js}
	 For scripting purposes inside the RPG Maker MV software

\paragraph{.json}
	 For storing various asset information inside the RPG Maker MV software













\pagebreak